---
title: "Funnel Plot Samples"
author: "Mike Pearson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Here we are calling the simplified `funnelslice` function using various parameters.

## Load the funnel library from github.

You'll need the devtools package.

```{r, echo = TRUE}
devtools::install_github('gmp26/funnel')
library(funnel)
load("../data/cabg.rda") # if necessary to access cabg data
x <- cabg # cabg was created by reading CABG-hospitals-03.csv into
``` 

### Small plots

Not so good yet!

```{r, echo = TRUE}
par(cex = 0.5)
funnelslice(x, plot_title = "Slice", plot = "slice")
par(cex = 0.5)
funnelslice(x, plot_title = "Funnel")
```

### Larger plots

In fact we need a figure size of about 7 inches wide, 6.5 inches high for a reasonable display. There's also an issue with margins in the slice mode.

```{r, echo = TRUE, fig.width = 7, fig.height = 6.5}
funnelslice(x, plot_title = "Slice", plot = "slice")
```

```{r, echo = TRUE, fig.width = 7, fig.height = 6.5}
funnelslice(x, plot_title = "Funnel")
```

### Lets get some test coverage...

```{r, echo = TRUE, dev = 'png', fig.width = 4}
funnelslice(x, plot_title = "Slice", plot = "slice", tails = c(0.01,0.05))
funnelslice(x, plot_title = "Funnel", tails = c(0.01,0.05))
```

```{r, echo = TRUE, dev = 'png', fig.width = 4}
funnelslice(x, plot_title = "Slice", plot = "slice", xlabel = "xlabel", ylabel = "ylabel")
funnelslice(x, plot_title = "Funnel", xlabel = "xlabel", ylabel = "ylabel")

```


```{r, echo = TRUE, dev = 'png', fig.width = 4}

funnelslice(x, plot_title = "Slice", plot = "slice",riskadj = T)
funnelslice(x, plot_title = "Funnel", riskadj = T)
```

###Notice the failed and missing funnel plot when riskadj  =  T above.

```{r, echo = TRUE, dev = 'png', fig.width = 4}

funnelslice(x, plot_title = "Slice", plot = "slice", RASRplot  =  T)
funnelslice(x, plot_title = "Funnel", RASRplot  =  T)
```

###Toggling the remaining booleans...

```{r, echo = TRUE, dev = 'png', fig.width = 4}
funnelslice(x, plot_title = "Slice", plot = "slice", mean.target = F, plot.target = T, ypercent = F)
funnelslice(x, plot_title = "Funnel", mean.target = F, plot.target = T, ypercent = F)


```

